Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-04-05 paper/paper-nature_format.qmd
more paper edits

This section is structured as follows. First, we provide an overview of our approach to understanding and parsing an individual Hansard XML document, which informed the scripts used to create our database. This will be supplemented with an excerpt from a Hansard XML to provide a visual example of its structure. Next we will explain the specific differences between the scripts, and outline what structural changes necessitated their separate development. We then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions. Finally, we discuss the script we developed to fill in remaining missing speaker details, which each file in our database was passed to after being parsed and cleaned.

@@

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child-nodes, where the first child-node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. The Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings between the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with `<business.start>` which is followed by a series of debates. Debate nodes can contain a `<subdebate.1>` child-node which has a `<subdebate.2>` child-node nested within it. That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the speaker and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will follow in @sec-qa.

@@

The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014. These contain all parsed text elements, where each statement is separated onto its own row with details about the speaker, and rows are maintained in chronological order. This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<sub-debate.1> versus`\<sub-debate.2\>\`. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. There were many intricacies in the task of splitting these speeches in a way that would be generalizable across sitting days. Details on these are provided in @sec-interject.

Since we are looking at a wide time span of documents, there are many changes in the way they are formatted. These became apparent as we ran our script on XML files from earlier sitting days. Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure. Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting. However, as mentioned, more significant changes in the XML structure of Hansard are what necessitated the development of separate scripts as we worked backwards. Further not every sitting day contains every possible XML element. For example, some days did not have `<sub-debate.2>` content, and some days did not have a Federation Chamber proceeding. To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element. For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse exists in the file.

@@

We then proceeded to clean up speeches and fill in correct speaker details. While we used the same lookup table approach as before, we did so in combination with another means of filling in speaker details. The patterns parsed from `<talk.start>` nodes contain important data on the speaker of each statement. As such, we could extract those data associated with each pattern by parsing one element inward, using the XPath expression `<talk.start/talker>`. We created a pattern lookup table with these data, and merged it with the main Hansard dataframe by the first pattern detected in each statement. @fig-patterns provides an example of that lookup table. This approach enabled us to fill in missing data on each speaker using data extracted directly from the XML. Finally, we then used the `AustralianPoliticians` dataset to fill in other missing data, and flagged for interjections in the same manner as before.

@@

While we did our best to maximize the completeness of the files in our database as they were processed in the initial four scripts, there were still a number of rows in which details on the person speaking were missing, or the name transcribed for that individual was in a short form (i.e. "Mr Abbott" instead of "Abbott, Tony, MP"). This was a particularly frequent occurrence for sitting days where a member spoke whose surname was shared by any other past or present member of parliament, and automated filling of their details using data from the `AustralianPoliticians` package was avoided to prevent any incorrect detail attribution. In an effort to improve as many of these as possible, we developed a script which identifies short-form names belonging to people with common surnames in each CSV, looks for the full version of that individuals name if available in that same CSV file, and replaces the short-form name with the full name, and fills the rest of the speaker details in accordingly with data from the `AustralianPoliticians` package. This script does the same for anyone who does have a unique surname but is still missing the full name form or any gender, unique ID, name ID, party or electorate details. Each file in our database passed through this script after being created, to ensure it is as complete as possible.

@@

Finally, our seventh test validates that all individuals speaking are active members of parliament on that particular day. We use the `mps` dataset from the `AustralianPoliticians` package which has the dates of each Member's duration in parliament. Using these dates, we check that each person speaking on each sitting day is in fact a Member of Parliament on that day.

@@

Finally, Hansard records contain a number of statements throughout that were not explicitly spoken in parliament. For example, the text in @fig-content_ex beneath the bold subtitle "Report from Federation Chamber" is not attributed to a particular member and was not spoken aloud during the parliamentary proceedings. In contrast, the text which comes afterward was spoken aloud in parliament by The Speaker at 14:01. Generally, unspoken text is nested under `<debate.text>` or `<subdebate.text>` nodes, while spoken text is categorized under `<speech>`. Importantly, in our work we focus primarily on parsing spoken speech content (i.e. what is nested within `<speech>` nodes), such as what is stated by The Speaker in @fig-content_ex. For this reason, many Hansard transcriptions which are not spoken text may not be captured in our database. In future work, capturing this unspoken content in our database would be a priority.

@@

Further, the `name.id` variable found in each CSV is another unique identifier for each Member of Parliament. This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook. As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook [@Leslie_2021_HoR_Aus]. This will allow for convenient extraction of further details on each Member of Parliament in a tidy, ready to analyze format.

>>>>

This section is structured as follows. First, we provide an overview of our approach to understanding and parsing an individual Hansard XML document, which informed the scripts used to create our database. This will be supplemented with an excerpt from a Hansard XML to provide a visual example of its structure. Next we will explain the specific differences between the scripts, and outline what structural changes necessitated their separate development. We then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions. Finally, we discuss the script we developed to fill in remaining missing details on the member of parliament speaking, which each file in our database was passed to after being parsed and cleaned.

@@

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child-nodes, where the first child-node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. The Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings between the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with `<business.start>` which is followed by a series of debates. Debate nodes can contain a `<subdebate.1>` child-node which has a `<subdebate.2>` child-node nested within it. That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the member of parliament whose turn it is to speak and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will follow in @sec-qa.

@@

The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014. These contain all parsed text elements, where each statement is separated onto its own row with details about the member of parliament who is speaking, and rows are maintained in chronological order. This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<subdebate.1>` versus `<subdebate.2>`. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by the Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. There were many intricacies in the task of splitting these speeches in a way that would be generalizable across sitting days. Details on these are provided in @sec-interject.

Since we are looking at a wide time span of documents, there are many changes in the way they are formatted. These became apparent as we ran our script on XML files from earlier sitting days. Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure. Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting. However, as mentioned, more significant changes in the XML structure of Hansard are what necessitated the development of separate scripts as we worked backwards. Further not every sitting day contains every possible XML element. For example, some days did not have `<subdebate.2>` content, and some days did not have a Federation Chamber proceeding. To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element. For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse exists in the file.

@@

We then proceeded to clean up speeches and fill in correct details on the member of parliament speaking. While we used the same lookup table approach as before, we did so in combination with another means of filling in these details. The patterns parsed from `<talk.start>` nodes contain important data on the member of parliament making each statement. As such, we could extract those data associated with each pattern by parsing one element inward, using the XPath expression `"talk.start/talker"`. We created a pattern lookup table with these data, and merged it with the main Hansard dataframe by the first pattern detected in each statement. @fig-patterns provides an example of that lookup table. This approach enabled us to fill in missing data on each member of parliament speaking using data extracted directly from the XML. Finally, we then used the `AustralianPoliticians` dataset to fill in other missing data, and flagged for interjections in the same manner as before.

@@

While we did our best to maximize the completeness of the files in our database as they were processed in the initial four scripts, there were still a number of rows in which details on the person speaking were missing, or the name transcribed for that individual was in a short form (i.e. "Mr Abbott" instead of "Abbott, Tony, MP"). This was a particularly frequent occurrence for sitting days where a member spoke whose surname was shared by any other past or present member of parliament, and automated filling of their details using data from the `AustralianPoliticians` package was avoided to prevent any incorrect detail attribution. In an effort to improve as many of these as possible, we developed a script which identifies short-form names belonging to people with common surnames in each CSV, looks for the full version of that individuals name if available in that same CSV file, and replaces the short-form name with the full name, and fills the rest of the MP details in accordingly with data from the `AustralianPoliticians` package. This script does the same for anyone who does have a unique surname but is still missing the full name form or any gender, unique ID, name ID, party or electorate details. Each file in our database passed through this script after being created, to ensure it is as complete as possible.

@@

Finally, our seventh test validates that all individuals speaking are active members of parliament on that particular day. We use the `mps` dataset from the `AustralianPoliticians` package which has the dates of each Member's duration in parliament. Using these dates, we check that each person speaking on each sitting day is in fact a member of parliament on that day.

@@

Finally, Hansard records contain a number of statements throughout that were not explicitly spoken in parliament. For example, the text in @fig-content_ex beneath the bold subtitle "Report from Federation Chamber" is not attributed to a particular member and was not spoken aloud during the parliamentary proceedings. In contrast, the text which comes afterward was spoken aloud in parliament by the Speaker at 14:01. Generally, unspoken text is nested under `<debate.text>` or `<subdebate.text>` nodes, while spoken text is categorized under `<speech>`. Importantly, in our work we focus primarily on parsing spoken speech content (i.e. what is nested within `<speech>` nodes), such as what is stated by the Speaker in @fig-content_ex. For this reason, many Hansard transcriptions which are not spoken text may not be captured in our database. In future work, capturing this unspoken content in our database would be a priority.

@@

Further, the `name.id` variable found in each CSV is another unique identifier for each member of parliament. This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook. As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook [@Leslie_2021_HoR_Aus]. This will allow for convenient extraction of further details on each member of parliament in a tidy, ready to analyze format.
